Manuscript

### 2015-06-15 inst/simulation/manuscript.Rmd
...

boundaryDF <- ggplot2::fortify(FinlandWTCStudy(context=context, response="canis.lupus")$studyArea$boundary)

@@

cutoff <- c(1,1000)

@@

```{r figure-5}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames, cutoff=Inf) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeCutoff=cutoff)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- rep(scenarioNames, times=2, each=length(modelNames))
  return(credibilityIntervals)  
}

cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames[c(1,3,5)], panel="Case 1", scenarioNames=scenarios, cutoff=cutoff)
#cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[c(1,3,5)], panel="Case 2", scenarioNames=scenarios, cutoff=10*cutoff)
#cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[c(1,3,5)], panel="Case 3", scenarioNames=scenarios, cutoff=cutoff)

plotCIProportions <- function(credibilityIntervals) {
  #modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$Model <- prettyModelName(credibilityIntervals$modelName)
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Model, colour=CI)) +
    geom_hline(aes(yintercept=.5), color="darkgrey") +
    geom_hline(aes(yintercept=.95), color="darkgrey") +
    geom_point(aes(shape=Model, group=Model), position=position_dodge(width=.7)) +
    scale_shape_manual("Model", values=c(17,15,3)) +
    scale_colour_manual("CI", values=c("gray", "black")) +
    #scale_colour_manual("Model", values=c("blue", "green", "red"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") + ylim(0, 1) +
    #facet_wrap(~panel) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0.2, 0.2, 0, 0), units="line"),
          #legend.background=element_rect(fill="transparent"),
          legend.margin=unit(-2, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom",
          legend.box="horizontal",
          legend.key.width=unit(.7, "line"))
  return(p)
}

cip <- cip1
#cip <- subset(rbind(cip1, cip2, cip3), modelName != "SmoothModel-nbinomial-ar1")
#cip <- subset(rbind(cip1, cip2, cip3), !(modelName %in% c("SmoothModel-nbinomial-ar1", "SmoothModel-nbinomial-matern-ar1")))
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", height=7.87/2)
saveFigure(p, "manuscript-figure-5.pdf", height=7.87/2, dpi=300)
```

>>>>

boundaryDF <- ggplot2::fortify(FinlandWTCStudy(context=context, response="canis.lupus")$studyArea$boundary)
cutoff <- c(1,1000)
```

@@

@@

```{r figure-5}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames, cutoff=Inf) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeCutoff=cutoff)
  credibilityIntervals <- list()

  if ("FMPModel" %in% modelNames) {
    for (scenario in scenarios) {
      study <- getStudy(scenario=scenario)
      validation <- Validation(study=study, populationSizeCutoff=cutoff)
      iterations <- validation$getCredibilityIntervalsValidationIterations("FMPModel")
      p95 <- c()
      p50 <- c()
      for (i in iterations) {
        load(file=validation$getCredibilityIntervalsValidationFileName(modelName="FMPModel", iteration=i))
        p95 <- c(p95, bootCI$p95)
        p50 <- c(p50, bootCI$p50)
      }
      a <- data.frame(scenario=scenario, Proportion=mean(p95, na.rm=T), n=NA, True=NA, Estimated=NA, Estimated.q1=NA, Estimated.q2=NA, modelName="FMPModel", Interval="95%")
      b <- data.frame(scenario=scenario, Proportion=mean(p50, na.rm=T), n=NA, True=NA, Estimated=NA, Estimated.q1=NA, Estimated.q2=NA, modelName="FMPModel", Interval="50%")
      credibilityIntervals <- rbind(credibilityIntervals, rbind(a, b))
    }
  }

  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames[!modelNames %in% "FMPModel"])
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames[!modelNames %in% "FMPModel"], probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(credibilityIntervals, rbind(a, b))
  credibilityIntervals$panel <- panel
  #credibilityIntervals$scenario <- rep(scenarioNames, times=2, each=length(modelNames))
  return(credibilityIntervals)

  #scenario=rep(scenarioNames, times=2, each=length(modelNames[!modelNames %in% "FMPModel"])))
}

cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames[c(1,3,4,5)], panel="Case 1", scenarioNames=scenarios, cutoff=cutoff)
#cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[c(1,3,5)], panel="Case 2", scenarioNames=scenarios, cutoff=10*cutoff)
#cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[c(1,3,5)], panel="Case 3", scenarioNames=scenarios, cutoff=cutoff)

plotCIProportions <- function(credibilityIntervals) {
  #modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$Model <- prettyModelName(credibilityIntervals$modelName)
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Model, colour=CI)) +
    geom_hline(aes(yintercept=.5), color="darkgrey") +
    geom_hline(aes(yintercept=.95), color="darkgrey") +
    geom_point(aes(shape=Model, group=Model), position=position_dodge(width=.7)) +
    scale_colour_manual("CI", values=c("black", "grey")) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") + ylim(0, 1) +
    #facet_wrap(~panel) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0.2, 0.2, 0, 0), units="line"),
          panel.margin=unit(0, units="line"),
          legend.margin=unit(-1, units="line"),
          #legend.position="bottom",
          legend.direction="horizontal",
          #legend.direction="vertical",
          legend.box="horizontal",
          legend.key.width=unit(.7, "line"),
          legend.key.height=unit(0, "line"))

  library(gridExtra)
  g_legend <- function(a.gplot) {
    tmp <- ggplot_gtable(ggplot_build(a.gplot))
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
    legend <- tmp$grobs[[leg]]
    legend
  }

  legend <- g_legend(p)
  p <- arrangeGrob(p + theme(legend.position="none"), legend, heights=c(9/10,1/10))
  return(p)
}

cip <- cip1
#cip <- subset(rbind(cip1, cip2, cip3), modelName != "SmoothModel-nbinomial-ar1")
#cip <- subset(rbind(cip1, cip2, cip3), !(modelName %in% c("SmoothModel-nbinomial-ar1", "SmoothModel-nbinomial-matern-ar1")))
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", height=7.87/2)
saveFigure(p, "manuscript-figure-5.pdf", height=7.87/2, dpi=300)
